\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-17 article.tex
add some comments

Given the image acquisition process, the fluorescent calcium time series
are smoothed using several linear and non linear filters in
order to reduce the imaging process effects. The overall filtering approach
is displayed at Figure \ref{fig:fitlering}.

\begin{figure}[bth]
\includegraphics[width=\linewidth]{images/fig_filtering}
\caption{Filtering steps. \textcolor{red}{TODO remake in pdf}}
\label{fig:filtered-signal}
\end{figure}

@@

Then we apply on the entire signal a non-linear filter based on the current
activity of the systems in order to favor the association measure inversely
proportional to the number of neurons firing together: $ x^{t,w}_i  =
(x^{t,d}_i + 1 )^{1 + \frac{1}{act_t}}$ where $act_t = \sum_{j} x^{t,d}_j$ is
the activity of all neurons at time $t$. When too much neurons are firing
together, i.e. in case of a network burst, it is almost impossible to retrieve
direct relationships: all neurons seem to be directly connected to each other.
By favoring the association measure when the activity is low, we expect to
retrieve a pair of neurons that are really directly connected together. In
concrete terms, as it can be verified on \textit{fig 1}, peak intensity may
change in function of the activity of all neurons but the number and the
locations of peaks is not modified.

>>>>

Given the image acquisition process, the fluorescent calcium time series
are smoothed using several linear and non linear filters in
order to reduce the imaging process effects. The overall filtering approach
is displayed at Figure \ref{fig:filtered-signal}.

\begin{figure}[bth]
\centering
\includegraphics[width=0.8\linewidth]{images/fig_filtering}
\caption{Filtering steps.}
\label{fig:filtered-signal}
\end{figure}

@@

After those 3 first filters, the fluorescence signal (Thresh. signal of
Figure \ref{fig:filtered-signal}) only contains clean spikes. However when a large
part of the network is firing, it's difficult to detect pairwise neuron
interactions. In order to reduce false interaction detection,
the signal is smoothed with a non-linear filter which penalizes
the filtered signal when a large part of the network is firing
\textcolor{red}{This equation doesn't correspond to the what we have done.}
\begin{align}
 x^{t,w}_i  &\leftarrow (x^{t,d}_i + 1 )^{1 + \frac{1}{\sum_{j} x^{t,d}_j}}.
\end{align}
Once this filtered has been applied (Weights signal of
Figure \ref{fig:filtered-signal}), peak intensities have
changed depending on the overall network activity, but not their numbers and
locations.

\textcolor{red}{PCA?}
